---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# scqe

<!-- badges: start -->
<!-- badges: end -->

The scqe package allows users to implement the stability controlled quasi-experiment (SCQE) (Hazlett, 2019) approach to study the effects of newly adopted treatments that were not assigned at random. This package contains tools to help users avoid making statistical assumptions that rely on infeasible assumptions.

## Motivation
Typical covariate-adjustment techniques used in statistical analysis impose the often too strict "no-unobserved confounding" assumption. Ignoring relevant cofounding biases can lead to overconfidence or inaccuracy of experimental results. SCQE instead imposes an assumption about the "baseline trend" for the change in average non-treatment outcome between successive cohorts in observational studies. More information about this method can be found in Hazlett, 2019.

## Installation


You can install the development version of scqe from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chadhazlett/scqe")
```
## Example
This is a basic example which shows you how to use the getSCQE function in order to obtain the scqe estimates and the se/CI for each delta.
The function allows for either a single value for delta or a vector of several values.

Say you have the following data. You have already determined your delta=.5
```{r}
#library(scqe)

#your data:
#we will use different data later, this is a sample for now
#the real data should eventually be stored in /data
set.seed(100)
my.data = data.frame(post=sample(c(0,1), replace=T,size=10), tmt=sample(c(0,1), replace=T,size=10), out=runif(10))
my.data
```

NOTE: this should not be here once the package is up and running
```{r}
library(AER)
getSCQE = function(post, treatment, outcome, delta){
    y2 = outcome - post %*% t(delta)
    r <- data.frame(term=numeric(length(delta)), estimate=numeric(length(delta)), conf.low=numeric(length(delta)),conf.high=numeric(length(delta)))
    for (i in 1:length(delta)){
      iv.out = summary(ivreg(y2[,i] ~ treatment | post))
      est = iv.out$coef["treatment",1]
      se = iv.out$coef["treatment",2]
      conf.low = est - 1.96*se
      conf.high = est + 1.96*se
      r[i,] = c(delta[i], est, conf.low, conf.high)
    }
    return(r)
  }
```


You wish to calculate the scqe estimates: sigle value of delta
```{r}
d = .5
getSCQE(my.data$post, my.data$tmt, my.data$out, d)
#"term" column signifies the delta corresponding to estimates in that line of the df
```

Let's say instead you want to get the scqe estimate for a range of values of delta: .5, .75, and 1
```{r}
d2 <- c(.5, .75, 1)
getSCQE(my.data$post, my.data$tmt, my.data$out, d2)
```
Since you fed the function a vector of deltas, it outputs a data frame with each row corresponding to a different delta or "term."




