---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# scqe

<!-- badges: start -->
<!-- badges: end -->

The scqe package allows users to implement the stability controlled quasi-experiment (SCQE) (Hazlett, 2019) approach to study the effects of newly adopted treatments that were not assigned at random. This package created tools to help users avoid making statistical assumptions that rely on infeasible assumptions.

## Motivation
Typical covariate-adjustment techniques used in statistical analysis impose the often too strict "no-unobserved confounding" assumption. Ignoring relevant cofounding biases can lead to overconfidence or inaccuracy of experimental results. SCQE instead imposes an assumption about the "baseline trend" for the change in average non-treatment outcome between successive cohorts in observational studies. More information about this method can be found in Hazlett, 2019.

## Installation


You can install the development version of scqe from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chadhazlett/scqe")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r}
#library(scqe)
## basic example code
```

